---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# counteR

<!-- badges: start -->
<!-- badges: end -->

The counteR contains only one function named `count_all_missing_by_group`. It is named `counteR` since the package can be expanded in the future in a way that provides general-purpose counting functions for data tables. For now, the goal of counteR is to group the given data table and count the missing (`NA`) values on the columns that are not `group` for each of the grouping results, according to the given group column(s). It creates a new table for that purpose and returns it.

## Installation

You can install the development version of counteR from [GitHub](https://github.com/) with using the following lines on your R terminal or files:

``` {r}
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/counteR")
```

## Syntax and Parameters:

```
count_all_missing_by_group(data, group_col, .groups="drop")
```
- data: the dataset you would use for the missing value counting
- group_col: the column(s) that the grouping will be performed on
- .groups: resulted data table's grouping condition, it follows the [`dplyr::summarize`](https://dplyr.tidyverse.org/reference/summarise.html) function's usage.

One can use `?count_all_missing_by_group` line in the R terminal to see the further documentation.

## Examples

This is how you can count the missing values on each of the columns despite the `group_col` of the specified column's groups with using `counteR`'s `count_all_missing_by_group` function (see the output tables' first few lines):

```{r example}
library(counteR)
# install.packages("datateachr")
library(datateachr) # for using the datasets

## basic example code
count_all_missing_by_group(steam_games, types) # according to the column type's groups, drops the groupings as it is the default behavior, you can use .groups = "drop" in order to do the same thing
count_all_missing_by_group(steam_games, types, "keep") # according to the column type's groups, keeps the groupings on the table
count_all_missing_by_group(chickwts, feed, "rowwise")
```

## Developer 

This package is developed using the conventions of [R Packages (2e)](https://r-pkgs.org) for the library structure. It is recommended to use the same conventions described by following links in order to contribute to this open-source package.

1. Testing: https://r-pkgs.org/testing-basics.html
2. R Code: https://r-pkgs.org/code.html
3. Description: https://r-pkgs.org/description.html
4. Licensing: https://r-pkgs.org/license.html
5. Function documentation: https://r-pkgs.org/man.html
6. Readme: https://r-pkgs.org/other-markdown.html


